---
title: "Literatur zusammenfassung"
author: "Philipp Franke"
date: "2023-01-28"
output:
  pdf_document: default

bibliography: literatur.bib
---

<!-- Einführung Rmarkdown Unigis: https://unigis-salzburg.github.io/Opt_AppDev-R/
Installation TinyTex:
 ```install.packages('tinytex')
 tinytex::install_tinytex()
 install.packages('rmarkdown')
 ```
-->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Literatur
## 1.
südliche populationsgrenzen von zwei molcharten. wassertemperatur inziziiert fortpflanzung.
* (i) how do the population dynamics of these two populations vary over their breeding period?
* (ii) How do environmental covariates (i.e., ground and water temperature, precipitation and photoperiod) affect the breeding-migration patterns in each species? And
* (iii) do individual traits, such as sex, body condition and body size (which can be considered a proxy for fecundity) influence these breeding-migration patterns? [@mettouris2018breeding]

## 2.
nördliche KM kommen jedes Jahr ins Fortpflanzungsgewässer. Erwachsen mit >2 Jahren (nur wenn schnell gewachsen) sind eher mit 3 oder 4. Überleben zwischen den Jahren zwischen 33-57 Prozent [@arntzen1993six]

## 3.
Untersuchungen in Bonn, 3 natürliche Weiher, 3 neu geschaffene, Weiher eingezäunt mit "drift fences"
adulte sind sehr weiher-treu, juvenile wandern <86m [@kupfer2000population]

# Literaturverzeichnis